Software Citation Principles

### 2016-03-24 sc-principles/software-citation-principles.tex
Unbreakable space before \cite{ascl}

In astronomy \& astrophysics: The Astronomy Source Code Library (ASCL) ~\cite{ascl}, is a website dedicated to the curation and indexing of software used in the astronomy-based literature. In 2015, the AAS and GitHub co-hosted a workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability and more recently, a Birds of a Feather session was held at the Astronomical Data Analysis Software and Systems (ADASS) XXV conference~\cite{2015arXiv151207919A} which included discussion of software citation.

>>>>

In astronomy \& astrophysics: The Astronomy Source Code Library
(ASCL)~\cite{ascl}, is a website dedicated to the curation and indexing of
software used in the astronomy-based literature. In 2015, the AAS and GitHub
co-hosted a workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability and more recently, a Birds of a Feather session
was held at the Astronomical Data Analysis Software and Systems (ADASS) XXV
conference~\cite{2015arXiv151207919A} which included discussion of software
citation.
